When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-13 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added equal contrib in authornote

---
title             : "When easy is not preferred: A discounting paradigm to assess load-independent task preference"
shorttitle        : "The CAD paradigm to assess task preference"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, credit.niso.org)
      - Conceptualization
      - Data curation
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role: 
      - Conceptualization
      - Resources
      - Supervision
      - Funding acquistion
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01062 Dresden, Germany"
authornote: |
abstract: |
  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  One approach to quantify the SVs of levels of difficulty of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
  We replicated the analysis of Westbrook and colleagues with an adapted version, the Cognitive and Affective Discounting (CAD) Paradigm.
  It quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
  Results show that many participants preferred a more or the most difficult level.
  Variance in SVs was best explained by a declining logistic contrast of the $n$-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
  Participants with higher Need for Cognition scores perceived higher $n$-back levels as less effortful and found them less aversive.
  Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences only emerged in higher levels.
  The CAD Paradigm appears to be well suited for assessing and analysing task preferences independent of the supposed objective task difficulty.

>>>>

---
title             : "When easy is not preferred: A discounting paradigm to assess load-independent task preference"
shorttitle        : "The CAD paradigm to assess task preference"
author: 
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "josephine.zerna@tu-dresden.de"
    equal_contrib : yes
    role:         # Contributorship roles (e.g., CRediT, credit.niso.org)
      - Conceptualization
      - Data curation
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft
      - Writing - review & editing
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    equal_contrib : yes
    role:
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Writing - review & editing
  - name          : "Corinna Kührt"
    orcid         : "0000-0002-6418-6479"
    affiliation   : "1"
    role:
      - Formal analysis
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role: 
      - Conceptualization
      - Resources
      - Supervision
      - Funding acquistion
      - Writing - review & editing
affiliation:
  - id            : "1"
    institution   : "Faculty of Psychology, Technische Universität Dresden, 01062 Dresden, Germany"
authornote        :
abstract          : |
  When individuals set goals, they consider the subjective value (SV) of the anticipated reward and the required effort, a trade-off that is of great interest to psychological research.
  One approach to quantify the SVs of levels of difficulty of a cognitive task is the Cognitive Effort Discounting Paradigm by Westbrook and colleagues (2013).
  However, it fails to acknowledge the highly subjective nature of effort, as it assumes a unidirectional, inverse relationship between task load and SVs.
  Therefore, it cannot map differences in effort perception that arise from traits like Need for Cognition, since individuals who enjoy effortful cognitive activities likely do not prefer the easiest level.
  We replicated the analysis of Westbrook and colleagues with an adapted version, the Cognitive and Affective Discounting (CAD) Paradigm.
  It quantifies SVs without assuming that the easiest level is preferred, thereby enabling the quantification of SVs for tasks without objective order of task load.
  Results show that many participants preferred a more or the most difficult level.
  Variance in SVs was best explained by a declining logistic contrast of the $n$-back levels and by the accuracy of responses, while reaction time as a predictor was highly volatile depending on the preprocessing pipeline.
  Participants with higher Need for Cognition scores perceived higher $n$-back levels as less effortful and found them less aversive.
  Effects of Need for Cognition on SVs in lower levels did not reach significance, as group differences only emerged in higher levels.
  The CAD Paradigm appears to be well suited for assessing and analysing task preferences independent of the supposed objective task difficulty.
